\begin{enumerate}
    \item Login
    \begin{itemize}
        \item When the login button is clicked. The server check the email and compare the password-hash 
        \item
        If the login input passed the validation, the user gets linked to the protected pages.
        \item
        Printing out error message when the validation failed
    \end{itemize}
    \item Register
    \begin{itemize}
        \item Validation of a User
        \begin{itemize}
            \item 
            A user is Valid, if the email is unique. That's means the server checks if a user with the email-input already exists. If not, it is a new user. After this process the server continue checking if all the require input fields are set and sends a status 200 to the client(front-end) if all is OK. 
        \end{itemize}
        
        \item After checking the validation, the server save the user into the database.
    \end{itemize}
    \item Main Interface
    \begin{itemize}
        \item Switching between the tab pages. Nicely done with the Ionic-Components.
    \end{itemize}
    \item Event page
    \begin{itemize}
        \item Left on the bottom there is a Ionicfabbutton. On click it displays a drop-down list with to another fab buttons. One to create events and one to join events.
        \item Displaying the created events
    \end{itemize}
    \item Home page
    \begin{itemize}
        \item Logout Button
        \item Some description about the application
    \end{itemize}
    \newpage
    \item Group page
    \begin{itemize}
        \item In "name-field" a user can type an event name. If he triggers the create button an event gets created and stored into the database referred to the user.
    \end{itemize}
    \item Settings page
    \begin{itemize}
        \item The UI is getting displayed on the setting page without any functionality
    \end{itemize}
\end{enumerate}